Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-10 latex/main.tex
Tables for deletion analysis

\begin{table}
\centering
\caption{
Major deletion events in the ARG.
These events are observed in more than 10,000 samples in the ARG.
}
\label{tab:major_dels}
\begin{tabular}{rrcrcrr}
\toprule
Start & Length & Region & Node & Pango & Count & Frequency (\%)\\
\midrule
28271 & 1 & non-coding & 1436808 & B.1 & 1118363 & 45.0561 \\
28248 & 6 & ORF8 & 220186 & B.1.617.2 & 1114669 & 44.9073 \\
22029 & 6 & S / S1 - NTD & 200039 & B.1.617.2 & 1112410 & 44.8163 \\
11288 & 4 & ORF1AB / NSP6 & 1436802 & B.1.1.529 & 871782 & 35.1220 \\
28362 & 9 & N & 1436802 & B.1.1.529 & 871774 & 35.1216 \\
21633 & 9 & S / S1 - NTD & 822854 & BA.2 & 532072 & 21.4359 \\
11292 & 5 & ORF1AB / NSP6 & 822854 & BA.2 & 531894 & 21.4287 \\
6513 & 3 & ORF1AB / NSP3 & 851246 & BA.1 & 340765 & 13.7286 \\
11283 & 5 & ORF1AB / NSP6 & 851246 & BA.1 & 339867 & 13.6924 \\
21765 & 6 & S / S1 - NTD & 851246 & BA.1 & 339681 & 13.6849 \\
21988 & 8 & S / S1 - NTD & 851246 & BA.1 & 339651 & 13.6837 \\
22194 & 3 & S / S1 - NTD & 851246 & BA.1 & 312706 & 12.5982 \\
28271 & 1 & non-coding & 86456 & B.1.1.7 & 290446 & 11.7014 \\
11288 & 9 & ORF1AB / NSP6 & 86456 & B.1.1.7 & 290408 & 11.6998 \\
21991 & 3 & S / S1 - NTD & 86456 & B.1.1.7 & 288831 & 11.6363 \\
21765 & 6 & S / S1 - NTD & 86456 & B.1.1.7 & 290438 & 11.7010 \\
21765 & 6 & S / S1 - NTD & 1265302 & BA.4 & 190425 & 7.6718 \\
28361 & 1 & N & 1246012 & BA.5.2.1 & 20822 & 0.8389 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{
Deletion events associated with the Alpha variant in the ARG.
These events occur above node 86456, which represents the origin of Alpha.
}
\label{tab:alpha_dels}
\begin{tabular}{rrcrr}
\toprule
Start & Length & Region & Count & Frequency (\%) \\
\midrule
28271 & 1 & non-coding & 290446 & 11.7014 \\
11288 & 9 & ORF1AB / NSP6 & 290408 & 11.6998 \\
21991 & 3 & S / S1 - NTD & 288831 & 11.6363 \\
21765 & 6 & S / S1 - NTD & 290438 & 11.7010 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Highly recurrent deletions.}
\label{tab:rec_dels}
\begin{tabular}{rrcr}
\toprule
Start & Length & Region & Occurrences \\
\midrule
29781 & 1 & non-coding & 12713 \\
29762 & 1 & non-coding & 11356 \\
29779 & 1 & non-coding & 10925 \\
29769 & 1 & non-coding & 10783 \\
29774 & 1 & non-coding & 10707 \\
29700 & 1 & non-coding & 8543 \\
29614 & 1 & ORF10 & 5041 \\
29555 & 1 & non-coding & 4816 \\
29543 & 1 & non-coding & 4806 \\
29541 & 1 & non-coding & 4804 \\
203 & 1 & non-coding & 3602 \\
222 & 1 & non-coding & 3441 \\
22013 & 6 & S / S1 - NTD & 2111 \\
21991 & 3 & S / S1 - NTD & 2087 \\
28254 & 1 & ORF8 & 1967 \\
27556 & 64 & ORF7a & 1281 \\
27579 & 3 & ORF7a & 1014 \\
28093 & 1 & ORF8 & 898 \\
21765 & 6 & S / S1 - NTD & 478 \\
27532 & 1 & ORF7a & 403 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption{Major deletion events in the ARG.}
\label{tab:major_dels}
\begin{tabular}{rrcrcrr}
\toprule
Start & Length & Region & Node & Pango lineage & Count & Frequency (\%)\\
\midrule
28271 & 1 & non-coding & 1436808 & B.1 & 1118363 & 45.0561 \\
28248 & 6 & ORF8 & 220186 & B.1.617.2 (Delta) & 1114669 & 44.9073 \\
22029 & 6 & S / S1-NTD & 200039 & B.1.617.2 (Delta) & 1112410 & 44.8163 \\
11288 & 4 & ORF1ab / NSP6 & 1436802 & B.1.1.529 & 871782 & 35.1220 \\
28362 & 9 & N & 1436802 & B.1.1.529 & 871774 & 35.1216 \\
21633 & 9 & S / S1-NTD & 822854 & BA.2 (Omicron) & 532072 & 21.4359 \\
11292 & 5 & ORF1ab / NSP6 & 822854 & BA.2 (Omicron) & 531894 & 21.4287 \\
6513 & 3 & ORF1ab / NSP3 & 851246 & BA.1 (Omicron) & 340765 & 13.7286 \\
11283 & 5 & ORF1ab / NSP6 & 851246 & BA.1 (Omicron) & 339867 & 13.6924 \\
21765 & 6 & S / S1-NTD & 851246 & BA.1 (Omicron) & 339681 & 13.6849 \\
21988 & 8 & S / S1-NTD & 851246 & BA.1 (Omicron) & 339651 & 13.6837 \\
22194 & 3 & S / S1-NTD & 851246 & BA.1 (Omicron) & 312706 & 12.5982 \\
28271 & 1 & non-coding & 86456 & B.1.1.7 (Alpha) & 290446 & 11.7014 \\
11288 & 9 & ORF1ab / NSP6 & 86456 & B.1.1.7 (Alpha) & 290408 & 11.6998 \\
21991 & 3 & S / S1-NTD & 86456 & B.1.1.7 (Alpha) & 288831 & 11.6363 \\
21765 & 6 & S / S1-NTD & 86456 & B.1.1.7 (Alpha) & 290438 & 11.7010 \\
21765 & 6 & S / S1-NTD & 1265302 & BA.4 (Omicron) & 190425 & 7.6718 \\
28361 & 1 & N & 1246012 & BA.5.2.1 (Omicron) & 20822 & 0.8389 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Highly recurrent deletions.}
\label{tab:rec_dels}
\begin{tabular}{rrcr}
\toprule
Start & Length & Region & Occurrences \\
\midrule
29781 & 1 & non-coding & 12713 \\
29762 & 1 & non-coding & 11356 \\
29779 & 1 & non-coding & 10925 \\
29769 & 1 & non-coding & 10783 \\
29774 & 1 & non-coding & 10707 \\
29700 & 1 & non-coding & 8543 \\
29614 & 1 & ORF10 & 5041 \\
29555 & 1 & non-coding & 4816 \\
29543 & 1 & non-coding & 4806 \\
29541 & 1 & non-coding & 4804 \\
203 & 1 & non-coding & 3602 \\
222 & 1 & non-coding & 3441 \\
22013 & 6 & S / S1-NTD & 2111 \\
21991 & 3 & S / S1-NTD & 2087 \\
28254 & 1 & ORF8 & 1967 \\
27556 & 64 & ORF7a & 1281 \\
27579 & 3 & ORF7a & 1014 \\
28093 & 1 & ORF8 & 898 \\
21765 & 6 & S / S1-NTD & 478 \\
27532 & 1 & ORF7a & 403 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Most commonly observed deletions in the ARG or Li et al. (2023).} 
\label{tab:common_dels}
\begin{tabular}{rrcrrrr}
\toprule
\multicolumn{3}{c}{} & \multicolumn{2}{c}{Sc2ts ARG} & \multicolumn{2}{c}{Li et al. (2023)} \\
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
Start & Length & Region & Count & Frequency (\%) & Count & Frequency (\%)\\
\midrule
28271 & 1 & non-coding & 1422469 & 57.3078 & 3853692 & 42.1183 \\
28248 & 6 & ORF8 & 1114712 & 44.9090 & 3026186 & 33.0742 \\
22029 & 6 & S / S1-NTD & 1114415 & 44.8970 & 3010665 & 32.9046 \\
11288 & 4 & ORF1ab / NSP6 & 871838 & 35.1242 & N/A & N/A \\
28362 & 9 & N & 871778 & 35.1218 & 3939164 & 43.0525 \\
21765 & 6 & S / S1-NTD & 825628 & 33.2625 & 3179887 & 34.7541 \\
21633 & 9 & S / S1-NTD & 532084 & 21.4364 & 1941962 & 21.2244 \\
11292 & 5 & ORF1ab / NSP6 & 531943 & 21.4307 & N/A & N/A \\
6513 & 3 & ORF1ab / NSP3 & 341714 & 13.7668 & 1984683 & 21.6913 \\
11283 & 5 & ORF1ab / NSP6 & 339935 & 13.6951 & 8360 & 0.0914 \\
21988 & 8 & S / S1-NTD & 339770 & 13.6885 & 590 & 0.0064 \\
22194 & 3 & S / S1-NTD & 313878 & 12.6454 & 1833050 & 20.0340 \\
11288 & 9 & ORF1ab / NSP6 & 311566 & 12.5522 & 3040576 & 33.2315 \\
21991 & 3 & S / S1-NTD & 308800 & 12.4408 & 912944 & 9.9779 \\
29762 & 1 & non-coding & 38030 & 1.5321 & N/A & N/A \\
29781 & 1 & non-coding & 36112 & 1.4549 & N/A & N/A \\
29769 & 1 & non-coding & 34315 & 1.3825 & N/A & N/A \\
29774 & 1 & non-coding & 33503 & 1.3498 & N/A & N/A \\
29779 & 1 & non-coding & 30515 & 1.2294 & N/A & N/A \\
11283 & 9 & ORF1ab / NSP6 & 60 & 0.0024 & 2011934 & 21.9891 \\
\bottomrule
\end{tabular}
\end{table}
